\documentclass[12pt,a4paper,oneside]{article}

\usepackage[margin=3cm]{geometry}

\usepackage{hyperref}
\hypersetup{
    pdftitle={Information Security},%
    pdfauthor={Toksaitov Dmitrii Alexandrovich},%
    pdfsubject={Syllabus},%
    pdfkeywords={syllabus;}{information;}{security;}{infosec},%
    colorlinks,%
    linkcolor=black,%
    citecolor=black,%
    filecolor=black,%
    urlcolor=black
}

\newcommand{\R}[1]{\uppercase\expandafter{\romannumeral #1\relax}}

\begin{document}

    \title{Information Security}
    \author{
        International University of Central Asia\\
        Information Technology Program
    }
    \date{}
    \maketitle

    \section{Course Information}

        \begin{description}
            \item[Course Repositories]\hfill\\
                \url{https://github.com/iuca/iuca-infosec}
            \item[Class Discussions]\hfill\\
                \url{https://piazza.com/iuca.kg/fall2018/iuca-infosec}
            \item[Place]\hfill\\
                TBD
            \item[Time]\hfill\\
                TBD
        \end{description}

    \section{Prerequisites}

        TBD

    \section{Contact Information}

        \begin{description}
            \item[Instructor]\hfill\\
                Toksaitov Dmitrii Alexandrovich\\
                \href{mailto:toksaitov_d@iuca.kg}{toksaitov\_d@iuca.kg}
            \item[Office]\hfill\\
                TBD
            \item[Office Hours]\hfill\\
                TBD
        \end{description}

    \section{Course Overview}
    
	In this introductory course on information security, students will learn about basic concepts, principles, and fundamental approaches to secure computers and various types of software and network systems.

    \section{Topics Covered}

        \begin{itemize}
        	\item Basics of information security
            \item Security management and risk assessment
            \item Desktop software security
            \item Web and mobile software security
            \item Operating systems security
            \item Network security
            \item Cryptography algorithms and protocols 
            \item Malware
            \item Privacy, legal and ethical issues
        \end{itemize}

    \section{Practice Tasks}

        Students are required to finish several practice tasks. The tasks are based
        on topics discussed during lectures.

    \section{Course Project}

        The course project will be to audit a working open-source system to find vulnerabilities and fix them. 

    \section{Final Exam}

        At the end of the course, students have to take the final examination in
        a form of a quiz with a number of multiple choice questions on topics
        discussed during classes.

    \section{Reading}

        \begin{enumerate}
            \item Applied Information Security: A Hands-on Approach, 1st edition by David Basin, Patrick Schaller, Michael Schläpfer (ISBN: 978-3642244735)
        \end{enumerate}

    \section{Grading}

        \begin{itemize}
            \item Practice tasks (30\%)
            \item Course project (40\%)
            \item Final examination (30\%)
        \end{itemize}

        \begin{itemize} \itemsep-10pt \parskip0pt \parsep0pt
            \item[--] 90\%--100\%: A\\
            \item[--] 80\%--89\%: A-\\
            \item[--] 70\%--79\%: B+\\
            \item[--] 65\%--69\%: B\\
            \item[--] 60\%--64\%: B-\\
            \item[--] 56\%--59\%: C+\\
            \item[--] 53\%--55\%: C\\
            \item[--] 50\%--52\%: C-\\
            \item[--] 46\%--49\%: D+\\
            \item[--] 43\%--45\%: D\\
            \item[--] 40\%--42\%: D-\\
            \item[--] Less than 39\%: F
        \end{itemize}

    \section{Rules}

        Students are required to follow the rules of conduct of the Information Technology Program and International University of Central Asia.

        Team work is NOT encouraged. Equal blocks of code or similar structural
        pieces in separate works will be considered as academic dishonesty and
        all parties will get zero for the task.

\end{document}

